Learning by Teaching a Robot:\\The Case of Handwriting

### 2016-01-18 main.tex
Removed Aude from co-author, at her request

\author{Séverin Lemaignan$^1$, Alexis Jacq$^{1,3}$, Deanna Hood$^1$, Fernando Garcia$^1$, \\
    Aude Billard$^2$, Ana Paiva$^3$, Pierre Dillenbourg$^1$ \\
$^1$CHILI Lab, École Polytechnique Fédérale de Lausanne, Switzerland,\\
$^2$LASA, École Polytechnique Fédérale de Lausanne, Switzerland,\\
$^3$Instituto Superior Técnico, University of Lisbon, Portugal}

>>>>

\author{Séverin Lemaignan$^1$, Alexis Jacq$^{1,2}$, Deanna Hood$^1$,\\Fernando
    Garcia$^1$, Ana Paiva$^2$, Pierre Dillenbourg$^1$ \\
$^1$CHILI Lab, École Polytechnique Fédérale de Lausanne, Switzerland,\\
$^2$Instituto Superior Técnico, University of Lisbon, Portugal}
